Graph Data Generators in the World of Big Data

### 2018-05-25 introduction.tex
edits on Section 1

To the best of our knowledge, our work is the first surveying the wide
landscale of graph data generators spanning different Big Data applications and 
targeting diverse computer science subfields. In particular, we cover graph database
generators, graph processing generators, social networks and community detection
generators, Semantic Web data generators, graph
analytics generators, IOT, Telecommunication and graph streaming generators, 
and Machine Learning and Graph Mining generators .

@@

\TODO{Outreach other surveys in other communities.}

@@

>>>>

To the best of our knowledge, our work is the first surveying the broad landscape of graph data generators spanning different Big Data applications and 
targeting diverse computer science subfields. In particular, we cover graph database
generators, graph processing generators, social networks and community detection
generators, Semantic Web data generators, graph
analytics generators, IOT, Telecommunication and graph streaming generators, 
and Machine Learning and Graph Mining generators. A comprehensive study of
graph generators is missing for many of the specific subfields mentioned
above.

@@

Graph generators matching graph patterns used in data mining have been
studied in \cite{Chakrabarti:2006:GML:1132952.1132954},
focusing on mostly occurring patterns, such as power laws, size of graph diameters
and community structure. The considered graph generators are compared in
terms of graph type, degree distributions, exponentiality, diameter and
community effects. We refer the reader to this survey for taxonomies
involving these properties, whereas we provide here a functionality-driven
taxonomy across all the categories of graph generators that we consider.

%\TODO{Outreach other surveys in other communities.}

@@

}
